Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-19 longoutput.tex
Wrap ground state check up as proof
Add TODOs from group discussion

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction for \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form. Then, NYI cuz we're stuck.

@@

@@

\begin{proof}
The proof is taken from \cite{quant-ph/0301040}. We consider the transform
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively. It is easy to check that this preserves $X$ and $Z$ measurement results.

@@

\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
	with ground state $\psi$ with the following properties:
	\begin{itemize}
		\item $\braket{\psi|H|\psi}=0$
		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	\end{itemize}
	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$. Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$. This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
\end{theorem}

@@

Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
Which is simple to estimate by picking and doing the measurements corresponding to $S$. The measurement result is $\pm1$. It can be modeled as a Bernoulli distribution with known expected value. The rest is simple number crunching.
\subsection{Analysis and amplification}

>>>>

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction of \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form. Then, NYI cuz we're stuck. \hannote{be more explicit}

@@

\KM{just use $n$ qubit input. no need to distinguish input vs ancilla at this point}

@@

\begin{proof}
\KM{prove what you claimed in the theorem.}

The proof is taken from \cite{quant-ph/0301040}. We consider the transform
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively. It is easy to check that this preserves $X$ and $Z$ measurement results.

@@

\KM{again, we don't need to make anccila explicit here}
\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item \KM{TODO} $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
	with ground state $\psi$ with the following properties:
	\begin{itemize}
		\item $\braket{\psi|H|\psi}=0$
		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	\end{itemize}
	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$. Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$. This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
\end{theorem}
\begin{proof}

@@

Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
Which is simple to estimate by picking and doing the measurements corresponding to $S$. The measurement result is $\pm1$. It can be modeled as a Bernoulli distribution with known expected value. The rest is simple number crunching.
\end{proof}

\subsection{Analysis and amplification}
